### 2019-08-14 README.Rmd
updated readme

- Can I remove some of the sources from the references file that I am not going to use?

@@

**app**

This folder contains files for Shiny app for visualizing the LIME explanations associated with the bullet land comparisons:

- `app.R`: code for the Shiny app

@@

- `helper_functions.R`: R script with functions that I use in the journals and will probably end up using in the papers as well

**data**

This folder is a location for storing raw and created data for the project:

- `hamby173and252_train.csv`: training data that I cleaned (it should match the data used to fit `rtrees`)
- `hamby224_bin_boundaries.rds`: contains the boundaries for the bins as created by the `lime` function for each of the LIME input settings from the single implementation 
- `hamby224_bins.rds`: contains nice forms of the bin intervals (i.e. [lower, upper)) created using the bin boundaries for each of the LIME input settings from the single implementation 
- `hamby224_explain`: the output from the `explain` function in lime from the single implementation with all of the different input options
- `hamby224_lime`: the output from the `lime` function in lime from the single implementation with all of the different input options
- `hamby224_lime_comparisons`: a dataset with summaries of the LIME explanations from the single implementation with all of the different input options
- `hamby224_lime_inputs`: LIME input settings used for the single implementation of LIME
- `hamby224_sensitivity_inputs`: LIME input settings used for the sensativity analysis of LIME
- `hamby224_sensitivity_joined.csv`: the test data and the LIME explanations from the sensativty analysis joined in a dataframe
- `hamby224_sensitivity_outputs.rds`: outputs from the `explain` function applied for each of the different input settings from the sensativity analysis combined in one dataframe
- `hamby223_test.csv`: testing data that I cleaned (created from sets 1 and 11 of the Hamby 224 study)
- `hamby224_test_explain.rds`: dataframe with the testing data and the output LIME explanation data from the single implementation with all of the different input options
- raw: original data given to me by Heike
    - `features-hamby173and252.csv`
    - `h224-set1-features.rds`
    - `h224-set11-features.rds`

@@

- `00-objectives_and_ideas`: background of the research project, goals of the project, concerns with LIME, and ideas to try
- `01-training_and_testing_data`: information on the Hamby data, understanding the raw data, and cleaning of the training and testing data
- `02-plotting_training_and_testing_data`: exploratory plots of the training and testing data
- `03-computation_issues`: documentation of some of the computation issues I ran into during the project
- `04-lime_algorithm_and_proposed_methods`: rough draft of the lime algorithm as implemented in the lime R package and proposed methods for improving the lime algorithm
- `05-applying_lime_to_rtrees`: application of lime and sensativity analysis for many different input options
- `06-assessing_lime_explanations`: assessment of the lime explanations
- `07-logistic_regression`: logistic regressions fit to the bullet data and application of lime to the logistic regression
- `08-iris_comparison`: applying LIME to a random forest fit to the iris data
- `09-understanding_lime`: attempts to visualize the results from LIME to understand how LIME works
- `10-other_explainers`: trying out other model explainers
- `notes from Heike.pdf`: scans of notes written by Heike for this project

**papers**

This folder contains the statistics and firearm examiners papers:

- `bullet_application`: explains how LIME can be used to understand the random forest model fit to bullet matching data
- `lime_diagnostics`: explains the need to assess LIME and presents some visual diagnostic tools

>>>>

@@

@@

- `app.R`: code for the Shiny app for visualizing the LIME explanations associated with the bullet land comparisons
- `helper_functions.R`: R script with functions that I use in the journals and will probably end up using in the papers as well

**figures**

This folder contains static images:

- `lime.png`: fun picture of a lime to use in the readme

@@

- `00-objectives_and_ideas`: background of the research project, goals of the project, concerns with LIME, and ideas to try
- `01-training_and_testing_data`: information on the Hamby data, understanding the raw data, and cleaning of the training and testing data
- `02-plotting_training_and_testing_data`: exploratory plots of the training and testing data
- `03-computation_issues`: documentation of some of the computation issues I ran into during the project
- `04-lime_algorithm_and_proposed_methods`: rough draft of the lime algorithm as implemented in the lime R package and proposed methods for improving the lime algorithm
- `05-applying_lime_to_rtrees`: application of lime and sensativity analysis for many different input options
- `06-assessing_lime_explanations`: assessment of the lime explanations
- `07-logistic_regression`: logistic regressions fit to the bullet data and application of lime to the logistic regression
- `08-iris_comparison`: applying LIME to a random forest fit to the iris data
- `09-understanding_lime`: attempts to visualize the results from LIME to understand how LIME works
- `10-other_explainers`: trying out other model explainers

**main**

The documents contained in the top folder are as follows:

- `.gitattributes`: attributes relating to git
- `.gitignore`: files to ignore
- `notes from Heike.pdf`: scans of notes written by Heike for this project
- `README`: document containing to do list and contents of this repository
